Verifying Demonstrations

### 2018-02-02 paper/SystemModel.tex
Minor edits to system model

Let us start by considering some examples.
During the demonstrations against the South Korean president in Seoul
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some 
  people stay\textins{ed} for several hours, others just several minutes%
}.
These rallies were all in the same location in the capital and repeated every 
weekend for the duration of a few weeks.
The Women's Marches~\cite{2017WomensMarchesInUS}, on the other hand, occurred 
in parallel in many locations.
We also have the Venezuelan demonstrations where
\blockcquote{2017VenezuelaProtestFrequency}{%
  anti-government demonstrators have staged daily protests across Venezuela%
} while
\blockcquote{AlJazeeraOnVenezuela2017}{%
  pro-government workers sang and danced as they staged a rival march to show 
  their support for the president's controversial plan to rewrite the 
  constitution%
}.
Judging from these examples, the minimal common part is the cause.%
\label{CauseIsTheCommonDenominator}

@@

The protests described above can be captured using this definition by splitting 
them up into subprotests.
Each subprotest will then be captured by our definition and to find the total 
we can just sum up the results.
The same for marches, the marching path can be divided into subprotests with 
coarse coordinates that slightly overlap.

@@

Each participant who want to be counted must submit a participation proof.
The proof must be associated with the protest, i.e.\ its identifier \(cid\), 
time and location.
We use witnesses to associate the proof to the location by creating a proof 
share.
A witness is only allowed to create one proof share per protester.
The proof and its proof shares are stored in a set, as there should be only 
unique proof shares.

\begin{frame}
\begin{definition}[Participation-proof share]
  A \emph{participation-proof share} \(w = (pid, cid, t, l, wid)\) is a tuple 
  where
  \(cid, t, l\) are as in \cref{DefProtest},
  \(pid\) is unique for a protester and \(cid\) pair, and
  \(wid\) is unique for a witness--protester pair.
  We let \(W\) be the set of all proof shares.
\end{definition}
\end{frame}

@@

The strength function \(s\) can be used to e.g.\ regulate trust in 
witnesses.
A trivial example would be for \(s\) to return the number of proof shares (i.e.\ 
witnesses) and thus let \(\theta\) to be the threshold of the number of required 
witnesses.

>>>>

Let us start by considering some examples.
During the demonstrations against the South Korean president in Seoul
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some 
  people stay\textins{ed} for several hours, others just several minutes%
}.
These rallies were all in the same location in the capital and repeated every 
weekend for the duration of a few weeks.
The Women's Marches~\cite{2017WomensMarchesInUS}, on the other hand, occurred 
in parallel in many locations.
We also have the Venezuelan demonstrations where
\blockcquote{2017VenezuelaProtestFrequency}{%
  anti-government demonstrators have staged daily protests across Venezuela%
} while
\blockcquote{AlJazeeraOnVenezuela2017}{%
  pro-government workers sang and danced as they staged a rival march to show 
  their support for the president's controversial plan to rewrite the 
  constitution%
}.
Judging from these examples, the minimal common part is the cause,%
\label{CauseIsTheCommonDenominator}
but there is also a location (or area) that varies over time.

@@

The protests described above can be captured using this definition by splitting 
them up into subprotests.
Each subprotest will then be captured by our definition and to find the total 
we can just sum up the results.
The same for marches, the marching path can be divided into subprotests with 
locations (or areas) that slightly overlap.

@@

Each participant who want to be counted must submit a participation proof.
The proof must be associated with the protest, i.e.\ its identifier \(cid\), 
time and location must coincide with any of its subprotests.
We use witnesses to associate the proof to the location by creating a proof 
share.
% XXX what is a witness?
A witness is only allowed to create one proof share per protester.
The proof and its proof shares are stored in a set, as there should be only 
unique proof shares.

\begin{frame}
\begin{definition}[Participation-proof share]
  A \emph{participation-proof share} \(w = (pid, cid, t, l, wid)\) is a tuple 
  where
  \(cid, t, l\) are as in \cref{DefProtest},
  \(pid\) is unique for a protester--\(cid\) pair, and
  \(wid\) is unique for a witness--protester pair.
  We let \(W\) be the set of all proof shares.
\end{definition}
\end{frame}

@@

The strength function \(s\) can be used to e.g.\ regulate trust in 
witnesses.
One example would be for \(s\) to return the number of proof shares (i.e.\ 
witnesses) and thus let \(\theta\) to be the threshold of the number of required 
witnesses.
